### 2012-03-15 docs/architecture/architecture.tex
more BCs

Each level has a {\tt phys\_bc\_level\_array(0:ngrids,dim,2)} array,
where {\tt ngrids} is the number of boxes on that level.  This stores
the physical desciption of the boundary type (outlet, inlet, slipwall,
etc.)---this description is independent of the variables that live on
the grid.  The {\tt phys\_bc\_level\_array(0,:,:)} `box' refers to the
entire domain.  If an edge of a box is not on a physical boundary,
then it is set to a default value (typically {\tt INTERIOR}).  
These boundary condition types are used to interpret the actual 
method to fill the ghostcells for each variable, as described in 
{\tt adv\_bc\_level\_array} and {\tt ell\_bc\_level\_array}.

The convention is that the first {\tt dm} variables in the
\bclevel\ refer to the velocity components, and the subsequent slots
are for the other standard variables described in the {\tt
  variables\_module}.  For instance, to reference the boundary
condition for density, one would index with {\tt dm+rho\_comp}.
For temporary variables that are created on the fly in the various
routines in \maestro\ there may not be a variable name in {\tt
  variables\_module} that describes the temporary variable.  In this
case, the special variables {\tt foextrap\_comp} and {\tt
  hoextrap\_comp} (first-order and high-order extrapolation) are used.

>>>>

Each level has a {\tt phys\_bc\_level\_array(0:ngrids,dim,2)} array,
where {\tt ngrids} is the number of boxes on that level and the last
index refers to the lower (1) or upper (2) edge of the box in the given
dimension.  This stores the physical desciption of the boundary type
(outlet, inlet, slipwall, etc.)---this description is independent of
the variables that live on the grid.  The {\tt
  phys\_bc\_level\_array(0,:,:)} `box' refers to the entire domain.
If an edge of a box is not on a physical boundary, then it is set to a
default value (typically {\tt INTERIOR}).  These boundary condition
types are used to interpret the actual method to fill the ghostcells
for each variable, as described in {\tt adv\_bc\_level\_array} and
{\tt ell\_bc\_level\_array}.

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, {\tt adv\_bc\_level\_array} describes the
{\em action} taken (e.g.\ reflect, extrapolate, etc.) for each
variable when filling boundaries.  {\tt adv\_bc\_level\_array} is
describes the boundary conditions that are in play for the advection
(hyperbolic) equations.  The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the new component,
{\tt nvar}, allows for each state variable that lives on a grid to
have different boundary condition actions associated with it.  The
convention is that the first {\tt dm} variables in the \bclevel\ refer
to the velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

{\tt ell\_bc\_level\_array} is the analog to {\tt adv\_bc\_level\_array}
for the elliptic solves in \maestro.  This will come into play in the
multigrid portions of the code.  The actions that are used for
{\tt ell\_bc\_level\_array} are either Dirichlet or Neumann boundary
condtions.
